Sell Prevention and Buy Cure: An Exploration of Indirect Conflicts

### 2013-12-11 iced-2013/paper.tex
ICED added reference to impact TR.
ICED added demographic table.

@@

We selected our interview participants from a large breadth of both open and closed source software development companies
and projects as well as Agile and Waterfall based projects.
The population which participated in our interview came from the following software groups: 
IBM, Mozilla, The GNOME Project, Microsoft Corporation, Subnet Solutions, Ruboss Technology Corporation, 
Amazon, Exporq Oy, Kano Apps, Fireworks Design, James Evans and Associates, and Frost Tree Games. 
Our participants were chosen based on their direct involvement in the actual writing of software for
their respective companies or projects. These participants' software development experience ranged from 3-25 years of experience
with an average of 8 years of experience.
In addition to software development, some participants were also chosen based on their experience with project management
at some capacity.

@@

Many indirect conflict tools have been created, tested, and published. Sarma et al.~\cite{Sarma:2007:TSA} created Palantir, 
which can both detect potential indirect conflicts, at the class signature level, and alert developers to these conflicts. 
Palantir represented one of the first serious attempts at aiding developers towards indirect conflicts. Holmes et 
al.~\cite{Holmes:2010:CAR} take it one step further with their tool YooHoo, by detecting fine grained source code changes, 
such as method return type changes, and create a taxonomy for different types of changes and their proneness to cause 
indirect conflicts. This tool and its taxonomy had a severely reduced false positive rate, however, the true positives 
detected may already be detectable by current tools such as compilers and unit testing. The tool Ariadne~\cite{Trainer:2005:BGT} 
creates an environment where developers can see how source code changes will affect other areas of a project at the 
method level, using method call graphs, showing where indirect conflicts may occur. This type of exploratory design has 
been used often in the visualization of indirect conflict tools, allowing developers a type of search area for their development
needs. Another indirect conflict tool, CASI~\cite{Servant:2010:CPI}, utilizes dependency slicing~\cite{Bajracharya:2009:SIS} 
instead of method call graphs to provide an environment to see what areas of a project are being affected by a source code change. 
Most of these tools have all shown to have the same common difficulties of scalability, false positives, and information overload, 
which were explored in this paper. Our own tool Impact!~\footnote{https://github.com/jordanell/Impact} also suffered these same fates.

>>>>

\usepackage{array} % for defining a new column type
\usepackage{varwidth} %for the varwidth minipage environment

@@

We selected our interview participants from a large breadth of both open and closed source software development companies
and projects as well as Agile and Waterfall based projects.
The population which participated in our interview came from the following software groups: 
IBM, Mozilla, The GNOME Project, Microsoft Corporation, Subnet Solutions, Ruboss Technology Corporation, 
Amazon, Exporq Oy, Kano Apps, Fireworks Design, James Evans and Associates, and Frost Tree Games. 
Our participants were chosen based on their direct involvement in the actual writing of software for
their respective companies or projects. These participants' software development experience ranged from 3-25 years of experience
with an average of 8 years of experience.
In addition to software development, some participants were also chosen based on their experience with project management
at some capacity. See Table~\ref{tab:demo} for more demographic details.

\begin{table*}[tb!]
\begin{center}
\begin{tabular}{| l | p{2cm} | p{2cm} | p{2cm} | p{2cm} | p{2cm} |}
\hline
Company & \# of Participants & Software Development Experience (years) & Development Process & Software Access & Current Language Focuses \\
\hline
\hline
Amazon & 2 & 5, 7 & Agile & Closed source & C++ \\ \hline
Exporq Oy & 1 & 8 & Agile & Closed source & Ruby, JavaScript \\ \hline
Fireworks Design & 1 & 6 & Agile & Closed source & JavaScript \\ \hline
Frost Tree Games & 1 & 4 & Agile & Closed source & C\# \\ \hline
GNOME & 1 & 13 & Agile & Open source & C \\ \hline
James Evans and Associates & 5 & 3, 3, 3, 4, 13 & Waterfall & Closed source & Oracle Forms \\ \hline
Kano Apps & 1 & 10 & Agile & Closed source & JavaScript, PHP \\ \hline
IBM & 2 & 5, 18 & Agile & Open and closed source & Java, JavaScript \\ \hline
Microsoft & 2 & 6, 10 & Agile & Closed source & C\# \\ \hline
Mozilla & 1 & 25 & Agile & Open source & C++, JavaScript \\ \hline
Ruboss & 1 & 5 & Agile & Closed source & JavaScript \\ \hline 
Subnet Solutions & 1 & 5 & Agile & Closed source & C++ \\ \hline

\end{tabular}
\end{center}
\caption{Demographic information of interview participants.\label{tab:demo}}
\end{table*}

@@

Many indirect conflict tools have been created, tested, and published. Sarma et al.~\cite{Sarma:2007:TSA} created Palantir, 
which can both detect potential indirect conflicts, at the class signature level, and alert developers to these conflicts. 
Palantir represented one of the first serious attempts at aiding developers towards indirect conflicts. Holmes et 
al.~\cite{Holmes:2010:CAR} take it one step further with their tool YooHoo, by detecting fine grained source code changes, 
such as method return type changes, and create a taxonomy for different types of changes and their proneness to cause 
indirect conflicts. This tool and its taxonomy had a severely reduced false positive rate, however, the true positives 
detected may already be detectable by current tools such as compilers and unit testing. The tool Ariadne~\cite{Trainer:2005:BGT} 
creates an environment where developers can see how source code changes will affect other areas of a project at the 
method level, using method call graphs, showing where indirect conflicts may occur. This type of exploratory design has 
been used often in the visualization of indirect conflict tools, allowing developers a type of search area for their development
needs. Another indirect conflict tool, CASI~\cite{Servant:2010:CPI}, utilizes dependency slicing~\cite{Bajracharya:2009:SIS} 
instead of method call graphs to provide an environment to see what areas of a project are being affected by a source code change. 
Most of these tools have all shown to have the same common difficulties of scalability, false positives, and information overload, 
which were explored in this paper. Our own tool 
Impact!~\footnote{University of Victoria Computer Science Technical Paper: DCS-351-IR} also suffered these same fates.
